---
title: "LBB-Classification2"
author: "annomitty"
date: "9/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> CALL LIBRARY

```{r}
library(caTools)
library(GGally)
library(caret)
library(e1071)
library(randomForest)
library(partykit)
```
> LOAD DATA

```{r}
bank <- read.csv2("bank.csv")
glimpse(bank)
colSums(is.na(bank))
```
Prediktor dan Penjelasannya :
1 - age (numeric)
2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
5 - default: has credit in default? (categorical: 'no','yes','unknown')
6 - housing: has housing loan? (categorical: 'no','yes','unknown')
7 - loan: has personal loan? (categorical: 'no','yes','unknown')
# related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone')
9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
# other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
14 - previous: number of contacts performed before this campaign and for this client (numeric)
15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

Target Variable:
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')

```{r}
summary(bank)
```
> SPLITTING DATASETS TO TRAINING AND TESTING.

```{r}
intrain <- sample(nrow(bank), nrow(bank)*0.8)
```

```{r}
bank_train <- bank[intrain, ]
bank_test <- bank[-intrain, ]
```

```{r}
dim(bank_train)
dim(bank_test)
```

> MODEL -> NAIVE BAYES

```{r}
model_naive <- naiveBayes(y ~ ., data = bank_train)
```

```{r}
bank_test_no_y <- bank_test[1:16]\
dim(bank_test_no_y)
```
```{r}
pred_naive <- predict(model_naive, newdata = bank_test_no_y)
```

```{r}
table_bayes <- table(pred_naive, bank_test$y)
confusionMatrix(table_bayes)
```
DENGAN MENGGUNAKAN NAIVE BAYES ACCURACY MODEL NYA ADALAH SEBESAR 85,6%

> MODEL -> DECISION TREE

```{r}
bank_train[sapply(bank_train, is.character)] <- lapply(bank_train[sapply(bank_train, is.character)], 
                                       as.factor)
  
```

```{r}
model_tree <- ctree(y~.,
                    bank_train,
                    control = ctree_control(mincriterion=0.8,
                                             minsplit=0.3,
                                             minbucket=0.3))
```

```{r, height=10}
model_tree
```
```{r}
pred_tree <- predict(model_tree, bank_test_no_y)
```

```{r}
table_tree <- table(pred_tree, bank_test$y)
confusionMatrix(table_tree)
```
DENGAN MENGGUNAKAN DECISION TREE MENDAPARKAN ACCURACY 89,5%

> MODEL  -> RANDOM FOREST

```{r}
bank[sapply(bank, is.character)] <- lapply(bank[sapply(bank, is.character)], 
                                       as.factor)
```

```{r}
bank2 <- bank
```


```{r}
glimpse(bank2)
```
```{r}
n0_var <- nearZeroVar(bank2)
bank2 <- bank2[,-n0_var]
```

```{r}
head(bank2)
```

```{r}
dim(bank2)
```
CROSS VALIDATION UNTUK RANDOM FOREST


```{r}
intrain <- sample(nrow(bank2), nrow(bank2)*0.8)
```

```{r}
bank2_train <- bank2[intrain, ]
bank2_test <- bank2[-intrain, ]
```

```{r}
bank2_train
```


PEMBUATAN MODEL RDS RANDOM FOREST

```{r}
#set.seed(123)

#ctrl <- trainControl(method = "repeatedcv",
                    number = 5, # k-fold
                    repeats = 3) # repetisi
#bank2_forest <- train(y ~ .,
                  data = bank2_train,
                  method = "rf", # random forest
                  trControl = ctrl)
#saveRDS(bank2_forest, "bank2_forest_2.RDS") # simpan model
```

```{r}
model_random <- readRDS("bank2_forest_2.RDS")
```

```{r}
pred_random <- predict(model_random, bank2_test)
```

```{r}
CM_random <- table(pred_random, bank2_test$y)
confusionMatrix(CM_random)
```
DENGAN MENGUNNAKN RANDOM FOREST METHOD MENDAPATKAN AKURASI SEBESAR 89,7%

KESIMPULANNYA:
ACCURACY NAIVE BAIYES         85,6%
ACCURACY DECISION TREE        89,5%
ACCURACY RANDOM FOREST        89,7%